Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

A evolving network $G_t(V,E_t)$ is stored in following contents:
\begin{itemize}
\item \textit{currentTime}, a non-negative real number.
\item \textit{edgeList}[$1\dots|V|$], an array that every of
whose entry points to a sorted array again, consisting the description of the
in edges of $v_i$ in the graph, each with elements:
\begin{itemize}
\item $u$, the other end point of the edge.
\item $t$, the time when this edge is added. (the array is sorted by $t$)
\item $w$, the weight of the edge, can be reduced if the network is unweighted.
\item $a$, the evolving activity of node $v_i$ at time $t$ after updating this
edge.
\end{itemize}

@@

\begin{algorithm}
\caption{\textsc{AddEdge}($v_i,v_j,t,w$)}
\textbf{Time Complexity:} $O(\log |V|)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $1\leq i,j\leq |V|$ and $t\geq currentTime$ and $w>0$.
\Ensure $G_t$ is up-to-date.
\State $\mathit{currentTime}\gets t$;
\State append ($j$,$t$,$w$) to \textit{edgeList}[$i$];
\State append ($i$,$t$,$w$) to \textit{edgeList}[$j$];
\If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
\State insert $j$ to \textit{edgeListReduced}[$i$] in appropriate position;
\State binary search $i$ on \textit{edgeListReduced}[$j$];
\State insert $i$ to \textit{edgeListReduced}[$j$] in appropriate position;
\EndIf
\State $p\gets \Call{FindRoot}{i}$;
\State $q\gets \Call{FindRoot}{j}$;
\If{$p\neq q$}
\State \Call{Merge}{$p$,$q$}
\EndIf
\end{algorithmic}
\end{algorithm}

The facility functions of union-find set is defined in follow.
\begin{algorithm}
\caption{\textsc{FindRoot}($i$)}
\textbf{Time Complexity:} $O(\log |V|)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $1\leq i\leq |V|$
\Ensure return the root of the union tree containing $v_i$.
\State $\mathit{currentTime}\gets t$;
\If {$\mathit{father}[i].u>0$}
	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
\Else
	\State \Return{$i$};
\EndIf
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{\textsc{Merge}($p$,$q$)}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $\mathit{father}[p].u<0$ and $\mathit{father}[q].u<0$
and $p\neq q$.
\Ensure Union trees $p$ and $q$.
\State $x \gets -\mathit{father}[p].u$;
\State $y \gets -\mathit{father}[q].u$;
\If {$x>y$}
	\State \Return{\Call{FindRoot}{$\mathit{father}[i]$}};
\Else
	\State \Return{$i$};
\EndIf
\end{algorithmic}
\end{algorithm}

>>>>

A evolving network $G_t(V,E_t)$ is stored in following contents:
\begin{itemize}
\item \textit{currentTime}, a non-negative real number.
\item $\mu$, a real number in range $(0,1)$.
\item $\eta$, a non-negative real number.
\item \textit{edgeList}[$1\dots|V|$], an array that every of
whose entry points to a sorted array again, consisting the description of the
in edges of $v_i$ in the graph, each with elements:
\begin{itemize}
\item $u$, the other end point of the edge.
\item $t$, the time when this edge is added. (the array is sorted by $t$)
\item $w$, the weight of the edge, can be reduced if the network is
unweighted.
\item $s$, the sum of all previous $w$, including this one.
\item $z$, the status variable for calculating the evolving activity of node
$v_i$ at time $t$ after updating this edge.
\end{itemize}

@@

The data type contains following functions:
\begin{itemize}
\item \textsc{Add Edge}($v_i,v_j,t,w$)

adds $e(v_i,v_j,t,w)$ to the graph and update the graph,
defined in Algorithm \ref{alg-add}.
\item \textsc{Query Degree}($t,v$)

returns $k(G_t,v)$, defined in Algorithm \ref{alg-deg}.
\item \textsc{Query Connectivity}($t,u,v$)

returns whether $u$ and $v$ is connected in the network at time $t$.
\item \textsc{Query Connectivity}($t,u,v$)

returns whether $u$ and $v$ is connected in the network at time $t$.
\item \textsc{Query Activity}($t,v$)

returns the evolving activity $a_{\mu,\eta}(G_t,v)$.
\item \textsc{Query Centrality}($t$, $\alpha$, $\beta$, $\mathbf{x}_0$, $m$)

returns the active centrality vector $\mathbf{x}(G_t)$. Algorithm
\ref{alg-cen} use the iteration method start with $\mathbf{x}_0$ and for
$m$ times.
\end{itemize}

\begin{algorithm}[htbp]
\caption{\textsc{AddEdge}($v_i,v_j,t,w$)}
\label{alg-add}
\textbf{Time Complexity:} $O(\log |V|)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $1\leq i,j\leq |V|$ and $t\geq \mathit{currentTime}$ and $w>0$.
\Ensure $G_t$ is up-to-date.
\State $\mathit{currentTime}\gets t$;
\State $z_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.z$;
\State $t_1\gets\mathit{edgeList}[i].\mathrm{lastElement}.t$;
\State $z_1\gets z_1+\mathit{currentTime}-t_1$;
\If {$z_1>0$} \State $z_1\gets 0$;\EndIf
\State $z_1\gets z_1-\eta\cdot w$;
\State $z_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.z$;
\State $t_2\gets\mathit{edgeList}[j].\mathrm{lastElement}.t$;
\State $z_2\gets z_2+\mathit{currentTime}-t_2$;
\If {$z_2>0$} \State $z_2\gets 0$;\EndIf
\State $z_2\gets z_2-\eta\cdot w$;
\State append ($j$,$t$,$w$,$z_2$) to \textit{edgeList}[$i$];
\State append ($i$,$t$,$w$,$z_1$) to \textit{edgeList}[$j$];
\If{ binary search on \textit{edgeListReduced}[$i$] did not find $j$}
\State insert $j$ to \textit{edgeListReduced}[$i$] in appropriate position;
\State binary search $i$ on \textit{edgeListReduced}[$j$];
\State insert $i$ to \textit{edgeListReduced}[$j$] in appropriate position;
\EndIf
\State $p\gets \Call{FindRoot}{i}$;
\State $q\gets \Call{FindRoot}{j}$;
\If{$p\neq q$}
\State \Call{Merge}{$p$,$q$}
\EndIf
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{FindRoot}($i$)}\label{alg1}
\textbf{Time Complexity:} $O(\log |V|)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $1\leq i\leq |V|$
\Ensure return the root of the union tree containing $v_i$.
\State $\mathit{currentTime}\gets t$;
\If {$\mathit{father}[i].u>0$}
	\State \Return{\Call{FindRoot}{$\mathit{father}[i].u$}};
\Else
	\State \Return{$i$};
\EndIf
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{Merge}($p$,$q$)}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\Require $\mathit{father}[p].u<0$ and $\mathit{father}[q].u<0$
and $p\neq q$.
\Ensure Union trees $p$ and $q$.
\State $x \gets -\mathit{father}[p].u$;
\State $y \gets -\mathit{father}[q].u$;
\If {$x>y$}
	\State $\mathit{father}[q].u\gets p$;
	\State $\mathit{father}[q].t\gets \mathit{currentTime}$;
	\State $\mathit{father}[p].u \gets \mathit{father}[p].u-y$;
\Else
	\State $\mathit{father}[p].u\gets q$;
	\State $\mathit{father}[p].t\gets \mathit{currentTime}$;
	\State $\mathit{father}[q].u \gets \mathit{father}[q].u-x$;
\EndIf
\end{algorithmic}
\end{algorithm}
